---
title: "rWorksheet_5"
author: "Rey Angelo Calopez BSIT 2-C"
date: "2023-12-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Create a data frame for the table below. Show your solution.
a. Compute the descriptive statistics using different packages (Hmisc and pastecs).
Write the codes and its result.
```{r}
StudentScore <- data.frame(Student = c(1,2,3,4,5,6,7,8,9,10),
                           PreTest = c(55,54,47,57,51,61,57,54,63,58),
                           PostTest = c(61,60,56,63,56,63,59,56,62,61))

StudentScore

#a.Compute the descriptive statistics using different packages (Hmisc and pastecs).
library(Hmisc)
library(pastecs)


HmiscStats <- describe(StudentScore[,c("PreTest","PostTest")])
HmiscStats

# Calculate descriptive statistics using pastecs
pastecsStats <- apply(StudentScore[,c('PreTest','PostTest')], 2, function(x)basic_stats(x))
pastecsStats

```
2. The Department of Agriculture was studying the effects of several levels of a fertilizer
on the growth of a plant. For some analyses, it might be useful to convert the fertilizer
levels to an ordered factor.
```{r}
library(dplyr)

fertilizerLevels <- c(10,10,10, 20,20,50,10,20,10,50,20,50,20,10)

orderedFactor <- factor(fertilizerLevels, levels = unique(fertilizerLevels))

basicStats <- summary(orderedFactor)
basicStats
```
3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the ex-
ercise levels undertaken by 10 subjects were “l”, “n”, “n”, “i”, “l” , “l”, “n”,

“n”, “i”, “l” ; n=none, l=light, i=intense
a. What is the best way to represent this in R?

```{r}
excerciseLevels <- c("n", "l", "n", "n", "l", "l", "n", "n", "i", "l")

ExerciseFactor <- factor(excerciseLevels, levels = c("n","l","i"))


basic_stats <- summary(ExerciseFactor)
basic_stats
```
4. Sample of 30 tax accountants from all the states and territories of Australia and their
individual state of origin is specified by a character vector of state mnemonics as:
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
"vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
"wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
"vic", "vic", "act")
a. Apply the factor function and factor level. Describe the results.
```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
"vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
"wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
"vic", "vic", "act")
stateFactor <- factor(state)
stateFactor

summaryState <- summary(stateFactor)
summaryState

```
5. From #4 - continuation:
• Suppose we have the incomes of the same tax accountants in another vector (in suitably
large units of money)
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
a. Calculate the sample mean income for each state we can now use the special function
tapply():
Example: giving a means vector with the components labelled by the levels
incmeans <- tapply(incomes, statef, mean)
Note: The function tapply() is used to apply a function, here mean(), to each group
of components of the first argument, here incomes, defined by the levels of the second
component, here state 2
```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)

meanIncome <- tapply(incomes, stateFactor, mean)
meanIncome

```
b.
6.Calculate the standard errors of the state income means (refer again to number 3)
stdError <- function(x) sqrt(var(x)/length(x))
Note: After this assignment, the standard errors are calculated by:
incster <- tapply(incomes, statef, stdError)
a. What is the standard error? Write the codes.
```{r}
stdError <- function(x) sqrt(var(x)/length(x))
incster <- tapply(incomes, state, stdError)
standardError <- tapply(incomes, stateFactor, stdError)
standardError
```
7. Use the titanic dataset.
a. subset the titatic dataset of those who survived and not survived. Show the codes
and its result.
```{r}


```